TODO (re-replication) (student) (cumulative science) (try again) (replication failure) 

### 2024-02-24 manuscript/manuscript.Rmd
mostly full very rough draft

---
title: "TODO (re-replication) (student) (cumulative science) (failure to replicate) "
author:
  - name: Veronica Boyce
    affiliation: Stanford
    footnote:
      - corresp
  - name: TODO
    affiliation: Stanford
  - name: Michael C. Frank
    affiliation: Stanford
address:
  - code: Stanford
    address: Stanford University
footnote:
  - code: corresp
    text: "Corresponding author. Email: vboyce@stanford.edu"
bibliography: ["251rescue.bib"] # Replace with one or more of your own bibtex files. Better BibTeX for Zotero is your friend
csl: apa6.csl # Use any CSL style. See https://www.zotero.org/styles for a good list. Ignored if citation_package: natbib
link-citations: TRUE
output:
  bookdown::pdf_document2:
    toc: FALSE
    keep_tex: TRUE
    template: generic_article_template.tex
    #md_extensions: "-autolink_bare_uris"
    number_sections: TRUE
    citation_package: default # Can also be "natbib"
lang: en # Main document language in BCP47 format
geometry: "margin=25mm"
papersize: a4
#linestretch: 2 # for double spacing
endfloat: FALSE # Set to TRUE to turn on latex endfloat package to place figures and tables at end of document
# endfloatoption: # See endfloat documentation for more possibilities
#   - tablesfirst # Default
#   - nomarkers # Default
numberlines: FALSE
authblk: TRUE # FALSE = author affiliations in footnotes; TRUE = author affiliations in a block below author names
footnotehyper: FALSE # TRUE will give you enhanced table footnote capabilities. Set to FALSE to be able to use French blocks. Needed due to what appears to be a latex bug.
urlcolor: blue
linkcolor: blue
citecolor: blue
graphics: TRUE # Needed to be able to include images
tables: TRUE # Needed to be able to include tables
# fancyhdr:
#   first:
#     #headleft: "REPORT-NO-XXXX"
#     headright: "Kaplan et al. (2021)"
#     headrulewidth: 0pt
#     #footleft: A left foot
#     footrulewidth: 0pt
#   subsequent:
#     #headleft: "NEXT-PAGE-HEADER-LEFT"
#     headright: "Kaplan et al. (2021)"
#     headrulewidth: 1pt
#     footrulewidth: 0pt

@@

TODO abstract
:::

@@

How definitive are failed replications?

While individual studies are not definitive when it comes to scientific evidence, they often influence what scientists pursue -- it worked -- keep going that direction, it didn't, possibly try again, or switch to a different question or method.

TODO cite the MB whatever that tried this.

Well, it depends on what you're trying to measure. From the perspective of learning from the field as a whole things are complicated and may depend also on a priori information from other related studies, the beleivability of the results, the relative rigor and sample sizes of the original and replication (TODO perhaps cite the time invariant).

Researchers do care about that from theory-building perspectives, but there's also a more local reason. Given that a student or lab has attempted a direct replication and that replication has not gotten the desired results of the original, what should they do? Should they try to replicate it again (potentially learning something about how to improve their experiment from the unsuccessful replication)? Or should they concluded that for them, given the resources they have, it isn't worth pursuing that particular experimental design?

Somewhere in here we should acknowledge that there's current discussion around replication rates and interpretation and so forth.

## Why replication failure? 
A replication can have different results from the original study for a number of different potential reasons. The original result may have been a fluke, through chance or p-hacking. The original result might be of much less generalizability than is assumed, and very sensitive to the exact conditions and time it was run in ("hidden moderators"). The original could have an inflated effect size, due to some combination of heterogeneity, p-hacking, luck, and publication bias. The replication could have been underpowered due to any of inflated original effect size, attrition in sample, or the original also being underpowered. A manipulation might have failed in the replication (this is a proximate cause that also raises the question of why the manipulation check failed). There might have been a difference in materials or instructions between the two, that turns out to matter (more likely if materials are not available). The experiment might not port well to online due to some details. A change in sample (ie. to online) may decrease data quality without sufficient attention checks. The replication might have made changes (for convenience or a new sample) that turn out to matter.

[list reasons] While one can theorize after the fact about potential causes, in most circumstances it is hard to diagnose for certain what made for the difference in the results. An exception might be if a specific error in one study or the other is found, such that the results were not what was thought (analytic error) or the data was not what was thought (experimental error).

@@

Heterogeneity and lack-of-generalizability reasons mostly suggest another failed replication, as the second replication is likely to be closer to the first replication than to the original in these random factors. CITE THAT PAPER about types of heterogeneity and which was they would fall

P-hacking and luck reasons are likely to suggest another failed replication.

@@

Changes between original and replication may or may not be fixable -- if the original materials are still unavailable, a second replication is no better off. If a second replication can get closer to the original, it might get more similar results.

Sensitivity to environment or not working well online are unlikely to be fixable if the replications remain constrained to using online methods.

These are pragmatic judgments related to how a lab might treat a failed replication as a sign that they cannot do cumulative science on a particular paradigm. In some cases, especially related to changes-in-population or changes-to-online, replications, and thus cumulative work on the paradigm, might be possible for other groups who have different resources.

The question is, having a failed replication, and not knowing which reasons might have caused the different results -- should a scientist try again?

## Current study
```{r}

@@

Here we report the results of `r num_proj` re-replication "rescue" projects which each re-replicated a study which had a failed or only partially-successful replication in @boyce2023. This is a non-random sample, and given the small number of projects, we provide descriptive statistics and discuss qualitatively some potential sources of differential re-replication outcomes.

@@

@@

library(kableExtra)
knitr::kable(cors, digits = 3, align='rcc', format="latex", booktabs=T, linesep="", caption="TODO CAPTION")

@@

Given that a couple of the successful rescues seemed to succeed in part because of larger sample sizes, we also added predictors related to the first replication sample size and the relative sizes of the samples (post-hoc, not pre-registered). 
While not signficant, the strongest correlates of rescue success were open materials, a small sample size on the first replication, a small sample size on the first replication relative to the original sample size, and a large rescue sample size relative to the first replication.

@@

```{r}
parsed_d |> select(name_pretty, type, N, closeness, replication_score) |> 
  filter(type!="additional") |> 
  pivot_wider(names_from="type", values_from=c(N, closeness, replication_score)) |> 
  select(paper=name_pretty, replication_score_rescue, N_original, N_rep1, N_rescue,
         "Replication \\\\  closeness"=closeness_rep1, closeness_rescue) |> arrange(replication_score_rescue|> desc()) |> knitr::kable(align="lllll", format="latex", booktabs=T, linesep="", caption="TODOCAPTION", col.names=c("", "", "Original", "Replication", "Rescue", "Replication", "Rescue")) |> add_header_above(c("Paper"=1, "Score"=1, "N"=3, "closeness"=2))

@@

@@

We first compare the original and replications effect sizes on the key effect of interest. Where possible, we report this comparison in standardized mean difference (SMD) units, although the reporting of a few studies makes comparison only possible in the original units. One potential issue with comparisons using SMD is that noisier measures will have smaller standardized effect sizes even if the effect on the original scale is the same. The effect sizes are shown in FIGURE TODO. In general, the replication and rescue effect sizes were smaller than the original effect sizes, and in a couple cases the effects were in the opposite direction.

@@

 all <- orig_v_others |> select(target_lastauthor_year, orig_v_other=d_p_orig) |> 
  left_join(orig_v_rescue |> select(target_lastauthor_year, orig_v_rescue=d_p_orig)) |> 
  left_join(orig_v_not_rescue |> select(target_lastauthor_year, orig_v_not_rescue=d_p_orig)) |> 
  left_join(rescue_v_reps |> select(target_lastauthor_year, rescue_v_reps=d_p_orig)) |> 
  rename(paper=target_lastauthor_year)

@@

rescue_rep_summ <- all |> ungroup() |> select(rescue_v_reps) |>
  summarize(median=median(rescue_v_reps, na.rm=T),
            low=quantile(rescue_v_reps, .25, na.rm=T),
            high=quantile(rescue_v_reps, .75, na.rm=T),
            less_than=sum(rescue_v_reps<.05, na.rm=T)/sum(!is.na(rescue_v_reps)))
```
## Consistency of effects 
We statistically compared the original effects with the replication effect sizes to determine their level of statistical consistency, that is whether these effects were likely to be drawn from the same distribution, given a certain level of heterogeneity.

We note that CITE! statistical consistency does not always align with our intuitions of replication or with whether an effect provides support for the hypothesis. A replication may be statistically consistent with the original effect but not provide any evidence for the claimed result.

@@

The median value of p_original was `r main_summ$median |> round(2)` [IQR: `r main_summ$low |> round(2)` - `r main_summ$high |> round(2)`]. `r round(main_summ$less_than*100)`% of the p_original values were less than .05, indicating by conventional thresholds a rejection of the null hypothesis that the original and the replications came from the same distribution for the given imputed level of heterogeneity.

@@

<!--* We will use p-original to evaluate how consistent the original effect size is with the totality of replications. We expect there to be a small number of replications, so we will impute the heterogeneity value as in https://osf.io/preprints/psyarxiv/dpyn6/. -->

We will visualize the consistency between original, 1st replication, rescue, and any other replications by plotting effect size and prediction interval for each. TODO how to actually do this!

@@

```{r, fig.height=6, fig.width=6}
colors <- c("original"="black", "rep1"="#377EB8", "rescue"="#E41A1C", "additional"="#984EA3")
shape <- c("original"=21,"rep1"=22,"rescue"=23,"additional"=24)
col_code <- c("TRUE"="darkgreen", "FALSE"="black")

@@

# Discussion
We don't have qualitative or quantitive explanations for why some replicated and some didn't. We can't predict what replication failures are likely to resolve given another try (or a more thoughtful try), beyond that suggestion that glaring problems and low samples may sometimes be resolvable.

So, if you have a replication that failed, in a topic you're interested in pursuing cumulative science on, should you drop it, or try again? Our sample says that the odds of a re-replication working are low, so especially if there isn't a super clear failure mode to point to, another try probably won't fix it.

Something about how even the "successes" have diminished effect sizes 
## Limitations
it's a small sample size and non-random 
Constraints on budget, timeline, and primarily online studies obviously constrain how closely and well some studies could be replicated. However, these are representative of the sort of limitations on early-career researchers. 
# Acknowledgements {-}

>>>>

---
title: "TODO (re-replication) (student) (cumulative science) (try again) (replication failure) "
author:
  - name: Veronica Boyce
    affiliation: Stanford
    footnote:
      - corresp
  - name: TODO
    affiliation: Stanford
  - name: Michael C. Frank
    affiliation: Stanford
address:
  - code: Stanford
    address: Stanford University
footnote:
  - code: corresp
    text: "Corresponding author. Email: vboyce@stanford.edu"
bibliography: ["251rescue.bib"] # Replace with one or more of your own bibtex files. Better BibTeX for Zotero is your friend
csl: apa6.csl # Use any CSL style. See https://www.zotero.org/styles for a good list. Ignored if citation_package: natbib
link-citations: TRUE
output:
  bookdown::pdf_document2:
    toc: FALSE
    keep_tex: TRUE
    template: generic_article_template.tex
    #md_extensions: "-autolink_bare_uris"
    number_sections: TRUE
    citation_package: default # Can also be "natbib"
lang: en # Main document language in BCP47 format
geometry: "margin=25mm"
papersize: a4
#linestretch: 2 # for double spacing
endfloat: FALSE # Set to TRUE to turn on latex endfloat package to place figures and tables at end of document
# endfloatoption: # See endfloat documentation for more possibilities
#   - tablesfirst # Default
#   - nomarkers # Default
numberlines: FALSE
authblk: TRUE # FALSE = author affiliations in footnotes; TRUE = author affiliations in a block below author names
footnotehyper: FALSE # TRUE will give you enhanced table footnote capabilities. Set to FALSE to be able to use French blocks. Needed due to what appears to be a latex bug.
urlcolor: blue
linkcolor: blue
citecolor: blue
graphics: TRUE # Needed to be able to include images
tables: TRUE # Needed to be able to include tables
# fancyhdr:
#   first:
#     #headleft: "REPORT-NO-XXXX"
#     headright: "Kaplan et al. (2021)"
#     headrulewidth: 0pt
#     #footleft: A left foot
#     footrulewidth: 0pt
#   subsequent:
#     #headleft: "NEXT-PAGE-HEADER-LEFT"
#     headright: "Kaplan et al. (2021)"
#     headrulewidth: 1pt
#     footrulewidth: 0pt

@@

TODO abstract
* cumulative science requires being able to replicate results
* given one failed replication, is a second attempt at replication likely to succeed?
We re-replicated 17 experiments that had previously had a failed student replication, reported in Boyce et al. (2023). In N/17 of these rescue projects (TODO %), the results mostly or fully replicated. We discuss the relative effect sizes and levels of statistical consistency between original effect sizes and replication effect sizes. 
While a few studies with failed replications were rescued with larger sample sizes and experimental tweaks, our overall results indicate that most failed replications stayed failed. If the goal is to do cumulative science, one may wish to stop after one failed replication. TODO MAKE THIS ABSTRACT BETTER!
:::

@@

Imagine the scenario where you are a new graduate student, and you run a replication of a study in the literature that you are interested in building upon in your research. The replication fails. Should you try again, running another replication, perhaps with a larger sample or other tweaks to possibly fix the replication? Or should you give up on replicating that specific study, and find a different study to replicate and build upon?

There has been much discussion in the literature about how we should interpret replication results in terms of the existence of a true effect or effect size. TODO CITATIONS

<!--Well, it depends on what you're trying to measure. From the perspective of learning from the field as a whole things are complicated and may depend also on a priori information from other related studies, the beleivability of the results, the relative rigor and sample sizes of the original and replication (TODO perhaps cite the time invariant). -->
We take a different angle on replications, and instead focus scientists decisions on what studies to run. Individual studies (and replications) are rarely definitive when it comes to scientific evidence, but they often influence what studies a scientist conducts.  If a study works, scientists are likely to continue to purse that result, but if a study doesn't work, scientists have to choose whether to try again, or switch to a different study.

How definitive is a replication failure? That is, if a study fails to replicate, what are the chances that an additional replication succeeds. After CITE OSF found an overall replication rate of WHATEVER, concerns were raised about some potential problems with some of the replications, that might have contributed to the replicaiton failures. TO address this ManyLABSWHATEVER NUMBER re-replicated N of these both independently and with ...

TODO READ THAT MANY LABS PAPER AGAIN.

## Why replication failure? 
The idea of replication failure implies a certain time direction: first a "successful" study and (later) a "failed" replication. (CITE TIME INVARIANCE) We can also consider this as two very-related studies that got different results, and thus the question is what difference between these two studies could account for the differing results.

[not sure if it would be better to structure this differently]

A replication can have different results from the original study for a number of different potential reasons. The original result may have been a fluke, through chance or p-hacking. The original result might be of much less generalizability than is assumed, and very sensitive to the exact conditions and time it was run in ("hidden moderators"). The original could have an inflated effect size, due to some combination of heterogeneity, p-hacking, luck, and publication bias.

The replication could have been underpowered due to any of inflated original effect size, attrition in sample, or the original also being underpowered. A manipulation might have failed in the replication (this is a proximate cause that also raises the question of why the manipulation check failed). There might have been a difference in materials or instructions between the two, that turns out to matter (more likely if materials are not available). The experiment might not port well to online due to some details. A change in sample (ie. to online) may decrease data quality without sufficient attention checks. The replication might have made changes (for convenience or a new sample) that turn out to matter.

While one can theorize after the fact about potential causes, in most circumstances it is hard to diagnose for certain what made for the difference in the results. An exception might be if a specific error in one study or the other is found, such that the results were not what was thought (analytic error) or the data was not what was thought (experimental error).

@@

Heterogeneity and lack-of-generalizability reasons mostly suggest another failed replication, as the second replication is likely to be closer to the first replication than to the original in these random factors. CITE THAT PAPER about types of heterogeneity and which way they would fall

If the original result was p-hacked or a luck false positive, then another replication is also likely to fail.

@@

Changes between original and replication may or may not be fixable -- if the original materials are still unavailable, a second replication is no better off. If a second replication can get closer to the original, either by using closer materials, or better adapting the study to a new environment, the rescue might succeed at better approximating the results of the original.

Sensitivity to environment or not working well online are unlikely to be fixable if the replications remain constrained to using online methods. Similarly, if the result is specific to a special population, then a new replication is also likely to fail, unless it has gained access to this population.

<!--These are pragmatic judgments related to how a lab might treat a failed replication as a sign that they cannot do cumulative science on a particular paradigm. In some cases, especially related to changes-in-population or changes-to-online, replications, and thus cumulative work on the paradigm, might be possible for other groups who have different resources.

The question is, having a failed replication, and not knowing which reasons might have caused the different results -- should a scientist try again? -->

Overall, it seems that there are both potential causes of replication failure that may be resolvable even with a similar level of resources and potential causes that are not resolvable, either at all, or given resource constraints.

## Current study

```{r}

@@

[Probably needs a better transition in] Here we report the results of `r num_proj` re-replication "rescue" projects which each re-replicated a study which had a failed or only partially-successful replication in @boyce2023. This is a non-random sample, and given the small number of projects, we provide descriptive statistics and discuss qualitatively some potential sources of differential re-replication outcomes.

@@

(could discuss tarampi as an example where there were potential issues, we fixed them and it still didn't work?)

@@

library(kableExtra)
knitr::kable(cors, digits = 3, align='rcc', format="latex", booktabs=T, linesep="", caption="Correlations between an individual predictor and the subjective replication score of the rescue project.")

@@

Given that a couple of the successful rescues seemed to succeed in part because of larger sample sizes, we also added predictors related to the first replication sample size and the relative sizes of the samples (post-hoc, not pre-registered). 
While not significant, the strongest correlates of rescue success were open materials, a small sample size on the first replication, a small sample size on the first replication relative to the original sample size, and a large rescue sample size relative to the first replication.

@@

```{r}
parsed_d |> select(name_pretty, type, N, closeness, replication_score) |> 
  filter(type!="additional") |> 
  pivot_wider(names_from="type", values_from=c(N, closeness, replication_score)) |> 
  select(paper=name_pretty, replication_score_rescue, N_original, N_rep1, N_rescue,
         "Replication \\\\  closeness"=closeness_rep1, closeness_rescue) |> arrange(replication_score_rescue|> desc()) |> knitr::kable(align="lllll", format="latex", booktabs=T, linesep="", caption="Comparison of sample size for original, replication, and rescue samples and measures of closeness for replication and rescue samples.", col.names=c("", "", "Original", "Replication", "Rescue", "Replication", "Rescue")) |> add_header_above(c("Paper"=1, "Score"=1, "N"=3, "closeness"=2))

@@

```{r, include=F, fig.cap="Standardized effect sizes of original studies, first replications, rescues, and additional replications if available. Due to the large effect size of a couple studies, large effect studies are shown in a separate panel. "}

smd_scale <- ggplot(for_plotting_d,aes(x=reorder(name_pretty, point, FUN=max),y=point,ymin=low,ymax=high,shape=type, color=type, fill=type, group=desc(type)))+
  geom_errorbar(size=.5,width=0, position=position_dodge(width=.5))+
  geom_point(position=position_dodge(width=.5))+
 coord_flip()+
  scale_size_area()+
  geom_hline(yintercept=0,color="black")+
    scale_color_manual(values=colors, aesthetics=c("color", "fill"))+
  scale_shape_manual(values=shape)+
  theme(legend.position = "bottom", 
        panel.grid.major.x = element_blank(), 
        panel.grid.minor.x=element_blank()
        )+
  labs(y="Standarized mean difference", x="")

smd_scale

@@

We first compare the original and replications effect sizes on the key effect of interest. We report this comparison in standardized mean difference (SMD) units. One potential issue with comparisons using SMD is that noisier measures will have smaller standardized effect sizes even if the effect on the original scale is the same. The effect sizes are shown in FIGURE TODO. In general, the replication and rescue effect sizes were smaller than the original effect sizes, and in a couple cases the effects were in the opposite direction.

@@

 all <- orig_v_others |> select(target_lastauthor_year, orig_v_other=d_p_orig) |> 
  left_join(orig_v_rescue |> select(target_lastauthor_year, orig_v_rescue=d_p_orig)) |> 
  left_join(orig_v_not_rescue |> select(target_lastauthor_year, orig_v_not_rescue=d_p_orig)) |> 
  left_join(rescue_v_reps |> select(target_lastauthor_year, rescue_v_reps=d_p_orig))

@@

rescue_rep_summ <- all |> ungroup() |> select(rescue_v_reps) |>
  summarize(median=median(rescue_v_reps, na.rm=T),
            low=quantile(rescue_v_reps, .25, na.rm=T),
            high=quantile(rescue_v_reps, .75, na.rm=T),
            less_than=sum(rescue_v_reps<.05, na.rm=T)/sum(!is.na(rescue_v_reps)))
```

```{r}
names <- parsed_d |> select(target_lastauthor_year, name_pretty) |> unique()

all |> ungroup() |>  left_join(names) |> select(Paper=name_pretty, `All reps`=orig_v_other, "Rescue" = orig_v_rescue, "Non-rescue"=orig_v_not_rescue, "Other reps"=rescue_v_reps) |> knitr::kable(format="latex", booktabs=T, linesep="", caption="P-original values between different sets of experiments. The primary analysis is between the original result and the meta-analytic aggregation of all replications. All p-originals assume an imputed heterogeneity value of tau=.21.", digits=3) |> 
  add_header_above(c(" "=1, "Original and"=3, "Rescue and"=1)) |> add_header_above(c(" "=1, "P-original comparing between"=4))

## Consistency of effects 
We statistically compared the original effects with the replication effect sizes to determine their level of statistical consistency, that is whether these effects were likely to be drawn from the same distribution, given a certain level of heterogeneity.

We note that statistical consistency does not always align with our intuitions of replication or with whether an effect provides support for the hypothesis [@patil2016]. A replication may be statistically consistent with the original effect but not provide any evidence for the claimed result.

@@

P-original values are shown in TABLE TODO. The median value of p_original was `r main_summ$median |> round(2)` [IQR: `r main_summ$low |> round(2)` - `r main_summ$high |> round(2)`]. `r round(main_summ$less_than*100)`% of the p_original values were less than .05, indicating by conventional thresholds a rejection of the null hypothesis that the original and the replications came from the same distribution for the given imputed level of heterogeneity.

@@

Visualizations of the statistical consistency between the original and each replication are shown in TODO FIGURE. The range around the open circle is the 95% predictive interval, representing the interval where, assuming that both are drawn from the same distribution, the replication will fall 95% of the time, given the precision (standard deviation) of the replication [@patil2016]. We again impute a heterogeneity value of $\tau=.21$ SMD for the construction of the prediction intervals.

<!--* We will use p-original to evaluate how consistent the original effect size is with the totality of replications. We expect there to be a small number of replications, so we will impute the heterogeneity value as in https://osf.io/preprints/psyarxiv/dpyn6/. --> 
Overall, a number of these rescues and replications are not statistically consistent with the original effects allowing for this level of heterogeneity.

@@

```{r, fig.caption="Plot of the prediction intervals of the original studies compared to replication results. The open circles are SMD effect sizes from the original studies, error bars are the prediction intervals, and filled shapes denote replication effect sizes. Prediction intervals in green contain the replication effect, those in grey do not. The largest effect sizes are separated in a separate panel to allow better visualization. "}
colors <- c("original"="black", "rep1"="#377EB8", "rescue"="#E41A1C", "additional"="#984EA3")
shape <- c("original"=21,"rep1"=22,"rescue"=23,"additional"=24)
col_code <- c("TRUE"="darkgreen", "FALSE"="black")

@@

# Discussion
We presented the results of `r num_proj` new replications that attempted to "rescue" previous failed replications reported in @boyce2023 by identifying possible causes of non-replication and ameliorating them. `r nrow(success)` of these replications (`r round(nrow(success)/num_proj*100)`%) mostly or fully replicated.

We don't have qualitative or quantitative explanations for why some replicated and some didn't. In a couple cases, increasing sample size and fixing internal validity issues in the replication seems to have led to a successful rescue (although we can't establish causality even in these cases). However, there were other studies that had small replication samples, or implementational deviations in the replication, and rescues were still unsuccessful. We can't predict what replication failures are likely to resolve given another try (or a more thoughtful try), beyond that suggestion that glaring problems and low samples may sometimes (but not always) be resolvable.

Another pattern we observed was that the effect sizes of even the successful replications tended to be substantially smaller than the original effect.

[SAY something about statistical consistency]

## Limitations
The reported rescue projects are a small sample of replications, and the effects explored are non-random, as they have been doubly selected by student interest. The authors of the rescue projects put substantial effort into trying to set up rescues that had a good chance of success, but projects were constrained by budget limitations, a short timeline, and primarily running online studies. These limitations are representative of the sort of resource limitations often faced by early-career researchers. That said, it is possible that different results might be obtained in better-resourced settings.

We opened this paper with a question about what an early-career researcher should do given a failed replication. Should one try again or move on? From our sample of testing the "try again" approach, it seems that the odds of a re-replication working are low, so especially if there isn't a super clear failure mode to point to, another try probably won't fix it.

# Acknowledgements {-}
